Perturbed Gait Data

### 2014-10-18 paper.tex

\usepackage{booktabs} % for table /toprule, /midrule, etc
\usepackage{todo}

@@

>>>>

\usepackage{graphicx}
\usepackage{booktabs} % for table /toprule, /midrule, etc
\usepackage{todo}

@@

Figure~\ref{fig:angle-torque-comparison} compares the mean and standard
deviation of saggital plane joint angles and torques from the perturbed gait
cycles and the unperturbed gait cycles computed from trial 20 for 120 gait
cycles. The variation in the dynamics is larger for the perturbed gait cycles.

\begin{figure}
  \includegraphics{figures/unperturbed-perturbed-comparison.pdf}
  \caption{Mean (solid, dashed) and $2\sigma$ (shaded) ($N=120$) joint angles
    and torques from both unperturbed (purple) and perturbed (blue) gait cycles
    from trial 20.}
  \label{fig:angle-torque-comparison}
\end{figure}

Figure~\ref{fig:gait-cycle-stats-comparison} compares the distribution in
several statistics of the unperturbed and perturbed gait cycles.

\begin{figure}
  \includegraphics{figures/unperturbed-perturbed-hist-comparison.pdf}
  \caption{Histograms of the average belt speed, cadence, step duration, and
    stride length which compare 120 gait cycles for the unperturbed (purple)
    and perturbed (blue).}
  \label{fig:gait-cycle-stats-comparison}
\end{figure}
